\documentclass[twoside,11pt]{article} % For LaTeX2e
\usepackage{jmlr2e}
\usepackage{hyperref}
\hypersetup{colorlinks,
	urlcolor=blue,
	citecolor=green,
	linkcolor=red}
\usepackage{url}
%\documentstyle[nips13submit_09,times,art10]{article} % For LaTeX 2.09
\usepackage{mathrsfs}
%\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
%\usepackage{amssymb}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{color}
\usepackage{mathtools}

\usepackage{pstricks}
\usepackage{tikz}
\usepackage{subcaption}

\begin{document}
	\noindent Dear Francis Bach, David M. Blei and Sch$\ddot{\mbox{o}}$lkopf: \\
	\medskip
	
	Me (Masum Billal) and my co-authors (Walid Khan, Farhad Alam) would like to submit our manuscript \textbf{Seeding in \texttt{k-means} Clustering} for publication in the Journal of Machine Learning Research. This paper talks about seeding techniques of \texttt{k-means} center initialization, shows comparison of performances and expresses some concerns about the results shown in \texttt{k-means++} paper.\\
	\medskip
	
	Each co-author is aware of this submission and consent to its review.  There are no conflicts of interest, since no co-author has recently collaborated with any action editor.
	\\
	\medskip
	
	Our suggestions for editors are those who have published papers related to \texttt{k-means} clustering method, specially in seeding initial centers. However, we would like to request excluding the authors of \texttt{k-means++} (in case they are part of the reviewing team). Because it would probably be a conflict of interest since the results shown in our paper (clear details are written in the paper) are in conflict with theirs.\\
	\medskip
	
	We have tried to follow the instructions presented in submission and author guidelines, common formatting errors and recommended practices by JMLR. We wrote the paper on top of the template provided in a JMLR page. Also, we have put in some extra effort so that we make less than a dozen mistakes (it was pointed out that most authors break at least a dozen formatting rules so we wanted to do better). We hope that our effort was not in vain and the number of mistakes is minimal in our paper preparation. If there is anything we have neglected to do in the submission process, please let us know and we will rectify the issue immediately. \\
	
	\medskip
	\noindent Thank you for your consideration, \\
	\medskip
	
	\noindent Masum Billal
\end{document}